### 2017-03-19 papers.tex
Incorporate author's revisions to 2017 paper 91
The citation links are now printed and there are no offending page numbers.

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{3cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{1cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{ZM\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

@@

\addtrack{Moose track}{Impure Math and \textbackslash Big Data}
\addpaper
	{Fake news logic}
	{Will Nalls}
	{}
	{SIGBOVIK_2017_paper_91}
	{1.85cm}
	{}
\addreview{SIGBOVIK_2017_review-91}{0cm}
\addpaper
	{RRR for UUU: Exact analysis of pee queue systems with perfect urinal etiquette}
	{Kristen Gardner and Ziv Scully}
	{}
	{SIGBOVIK_2017_paper_75}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-75}{0cm}
\addpaper
	{The next 700 type systems}
	{Carlo Angiuli}
	{}
	{SIGBOVIK_2017_paper_33}
	{3cm}
	{}
\addpaper
	{A modular approach to state-of-the-art big data visualization}
	{Keith A.\ Maki}
	{}
	{SIGBOVIK_2017_paper_78}
	{0cm}
	{}
\addpaper
	{Efficient computation of an optimal portmantout}
	{David Renshaw}
	{}
	{SIGBOVIK_2017_paper_34}
	{0cm}
	{}

>>>>

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{3cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{1cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{ZM\~{}\~{}\ \#\ \ \ \ \ \ \ \ PRinty\#\ \ \ \ \ C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

@@

\addtrack{Moose track}{Impure Math and \textbackslash Big Data}
\addpaper
	{Fake news logic}
	{Will Nalls}
	{}
	{SIGBOVIK_2017_paper_91}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-91}{0cm}
\addpaper
	{RRR for UUU: Exact analysis of pee queue systems with perfect urinal etiquette}
	{Kristen Gardner and Ziv Scully}
	{}
	{SIGBOVIK_2017_paper_75}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-75}{0cm}
\addpaper
	{The next 700 type systems}
	{Carlo Angiuli}
	{}
	{SIGBOVIK_2017_paper_33}
	{3cm}
	{}
\addpaper
	{A modular approach to state-of-the-art big data visualization}
	{Keith A.\ Maki}
	{}
	{SIGBOVIK_2017_paper_78}
	{0cm}
	{}
\addpaper
	{Efficient computation of an optimal portmantout}
	{David Renshaw}
	{}
	{SIGBOVIK_2017_paper_34}
	{0cm}
	{}
